Comparing the Jacobi Method and LLL lattice reduction algorithms for cryptographic applications

### 2014-12-08 report/paper.tex
small typo

\end{algorithmic}
\end{algorithm}
my{some v's and u's at three positions seem stroll around in the above algorithm}

@@

\STATE{$q \leftarrow \lfloor \frac {\vec{G}_{ii}}{\vec{G}_{ss}} \rceil $ my{better work with s and l as indices}}

>>>>

\end{algorithmic}
\end{algorithm}
\my{some v's and u's at three positions seem stroll around in the above algorithm}

@@

\STATE{$q \leftarrow \lfloor \frac {\vec{G}_{ii}}{\vec{G}_{ss}} \rceil $ \my{better work with s and l as indices}}
